Cross Validation Approaches for Penalized Cox Regression

### 2018-11-14 main.tex
some wording/citation changes

\par Cross-validation is one of the most common methods used to select the appropriate $\lambda$ for penalized regression models. Suppose a data set $D$ of n observations is partitioned into $K$ folds: $D_{1}, D_{2}, ... D_{K}$. For a given $k \in \left\{1,2, ... , K\right\}$, set $T_{k} = D - D_{k}$. Then, we consider $T_{k}$ as the training set and $D_{k}$ as the test set. This manuscript is concerned with the question: how should one use the $kth$ fold $D_{k}$ to measure predictive accuracy based on partial likelihood? In the following sections, we use $L^{-k}$ to denote the partial likelihood when it is built over data in $T_k$; $L^{k}$ when it is built over data in $D_k$; and $L$ when it is built over the entire data set $D$.  The log partial likelihood is denoted by lower case $l$. For individual subject's contribution to the likelihood, we use $L_i$, where $i$ denotes the individual. Particularly of our interest, if $L^{-k}(\beta)$ is used in \eqref{eq:obj} to obtain penalized likelihood estimates using data in $T_k$, we use $\hat{\beta}^{-k}$ to denote the penalized estimates that are obtained.

@@

  %Need to update this section with the new baseline estimation method%
The fundamental challenge of conducting cross validation for cox regression is that the baseline hazard is not estimated from the model. Hence we proposed our next approach based on getting the baseline hazard $\hat{\Lambda}_{0}$. We would first obtain cross-validated linear predictors $\hat{\eta}^{cv}$ from $D_k$ in the same way as the previous approach. With $\hat{\eta}^{cv}$,  a cross-validated version of baseline hazard $\hat{\Lambda}^{cv}_{0}$ that uses all observations can be estimated via Kalbfleisch and Prentice's method \citep{Kalbfleisch2011}.

As an analogue to the residual sum of squaires in linear regression, we considered using the sum of squared Martingale residuals, preferably its normalized form, deviance residuals, to measure the model's predictive accuracy \citep{Therneau1990}. First proposed for model diagnosis, deviance residuals have also been used as a predictive accuracy measure in survival tree models \citep{Therneau2018}. Given that the baseline hazard and linear predictors are obtained via cross-validation, we can first obtain the cross-validated Martingale residual: 
	\begin{equation}
	\hat{M^{cv}_{i}} = \delta_{i} -\hat{\Lambda}^{cv}_{0}(t_{i})e^{\hat{\eta}^{cv}_{i}},
	\end{equation} 
where $\delta_{i}$ is the status of the $ith$ observation and $t_{i}$ is the time component of the $ith$ observation. The cross-validated deviance residuals can then be derived from the Martingale residuals: 
	\begin{equation} 
	d_{i} = sgn(\hat{M}^{cv}_{i})(-2(\hat{M}^{cv}_{i} + \delta_{i}log(\delta_{i} - \hat{M}^{cv}_{i})))^{1/2}.
	\end{equation}
The sum of squared cross-validated deviance residuals, $\sum_{i}\hat{d}_{i}^2$ are used as the cross validated error. We refer this approach as the \emph{cross-validated deviance residuals}.

@@

\par We first measure the distance between the fitted model and the true model via mean squared error of the coefficients. Suppose $\hat{\beta}(\lambda)$ is the set of coefficients estimated by a cox model with LASSO penalty at $\lambda$. Mean squared error $MSE$ is defined to be 
\begin{equation}
E(\hat{\beta}(\lambda) - \beta)^2
\end{equation}
For each generated data set, an oracle model would be fitted using Cox regression only upon variables that are set as non-zero in the data generating process. The resulted estimates would be denoted by $\hat{\beta}^{oracle}$. Then the models selected by the cross validation methods with $\lambda^{cv}$ would be compared to the oracle model via 
\begin{equation}
log\left\{ \frac{MSE(\hat{\beta}(\lambda^{cv}))}{MSE(\hat{\beta}^{oracle})} \right\}
\end{equation}
for each cross-validation selected $\lambda^{cv}$ in each generated data set. The results would be averaged over N replications.

@@

\par While the MSE, Brier Score and Kullback-Leibler Score are good measures of the model, they are not very interpretable. Hence, we included Harrell's C Index as the last measure of the predictive accuracy\citep{HarrellJr1984}. The C Index is a rank-based statistic that measures the concordance between the linear predictor of the selected model and the observed outcome. Suppose we arbitrarily take two observation out of the data. If the observation that has a greater prognostic score also has a greater risk or shorter survival time until the event occur, then this would be considered as a concordant pair. C Index estimates of proportion of concordance pairs in the data set. It has a range between 0.5 and 1. Where C Index of 0.5 means the prediction is as as good as flipping a coin and Index of 1 means perfect concordance. We also computed Harrell's C Index upon the independent test set for all four models selected by cross-validation and averaged over all replications.

The simulation experiments were first conducted when the signal in the data was varied. In each simulated data set, there are n = 150 observations and p = 1000 covariates. 10$\%$ of the observations were censored. 10-fold cross-validation was implemented for all four methods. Number of non-zero $\beta$s was 10. The signal in the data set was varied by varying the magnitude of the $\beta$s from 0.4 to 0.9. For each scenario, 200 replications were used.

@@

\par Results of the simulation were illustrated in Figure 2. The x axis of the plots are the magnitude of the non-zero $\beta$ coefficients. The left panel compares the MSE ratios of the models selected.  The y-axis represents the MSE ratios between the cross-validation selected models and the optimal model. The standard method has the smallest MSE ratio. The linear predictor approach's performance is also very close the standard approach. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater MSE. The middle panel compares the Brier scores of the models selected. The y-axis represents the Brier score. The standard method and the linear predictor approach have lower brier score across all levels of signals. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater Brier scores. The left panel compares Harrell's C of the models selected. The y-axis represents Harrell's C, which increases from around 0.6 to 0.8 as the coefficent size increases. The standard method and the linear predictor approach have slightly higher Harrell's C across all levels of signals, indicating better prediction accuracy. Overall, all four methods have very close performance .

@@

\caption{\label{tab:} Simulation Studies that Compare All Four Cross-Validation Methods Varying Dimension and Signal }
\centering
\begin{tabular}[t]{cccccccccc}
\toprule
 n& p& $\#$ Non-Zero & Signal & Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
150 & 50 & 5 & 0.3 & V VH  & 0.095 (0.028) & 1.457 (0.954) & 0.242 (0.013) & 0.678 (0.029) & 0.617 (0.034) \\
    &    &   &     & Standard  & 0.087 (0.030) & 1.459 (0.922) & 0.242 (0.013) & 0.678 (0.029) & 0.618 (0.032) \\
    &    &   &     & LinearPred  & 0.088 (0.025) & 1.433 (0.927) & 0.241 (0.013) & 0.677 (0.028) & 0.620 (0.029) \\
    &    &   &     & DevResid  & 0.132 (0.032) & 1.676 (1.019) & 0.248 (0.014) & 0.689 (0.030) & 0.601 (0.044) \\
\addlinespace
150 & 50 & 5 & 0.6 & V VH  & 0.070 (0.011) & 1.733 (0.922) & 0.177 (0.012) & 0.527 (0.030) & 0.750 (0.014) \\
    &    &   &     & Standard  & 0.066 (0.012) & 1.688 (0.909) & 0.176 (0.012) & 0.526 (0.029) & 0.749 (0.014) \\
    &    &   &     & LinearPred  & 0.067 (0.011) & 1.695 (0.925) & 0.176 (0.012) & 0.526 (0.030) & 0.750 (0.014) \\
    &    &   &     & DevResid  & 0.110 (0.012) & 2.339 (0.868) & 0.187 (0.014) & 0.554 (0.033) & 0.750 (0.018) \\
\addlinespace
300 & 10000 & 20 & low & V VH  & 0.139 (0.021) & 3.463 (0.438) & 0.244 (0.015) & 0.681 (0.032) & 0.612 (0.051) \\
    &    &   &     & Standard  & 0.105 (0.027) & 3.350 (0.458) & 0.228 (0.021) & 0.646 (0.045) & 0.639 (0.05) \\
    &    &   &     & LinearPred  & 0.107 (0.026) & 3.360 (0.462) & 0.229 (0.021) & 0.648 (0.045) & 0.638 (0.049) \\
    &    &   &     & DevResid  & 0.139 (0.027) & 3.454 (0.447) & 0.243 (0.018) & 0.678 (0.038) & 0.610 (0.058) \\
\addlinespace
500 & 10000 & 20 & strong & V VH  & 0.072 (0.005) & 3.469 (0.480) & 0.162 (0.015) & 0.495 (0.036) & 0.784 (0.021) \\
    &    &   &     & Standard  & 0.056 (0.005) & 3.174 (0.504) & 0.153 (0.011) & 0.465 (0.029) & 0.782 (0.017) \\
    &    &   &     & LinearPred  & 0.057 (0.005) & 3.204 (0.498) & 0.153 (0.011) & 0.466 (0.029) & 0.783 (0.017) \\
    &    &   &     & DevResid  & 0.076 (0.005) & 3.545 (0.467) & 0.167 (0.015) & 0.508 (0.035) & 0.782 (0.022) \\
\bottomrule
\end{tabular}
\end{table}

\par Additional simulation studies were conducted for other four scenarios, which a combination of different dimensions and signal in the data. The results are shown in Table 1. More specifically, we examined low dimension (p = 50) with weak signal, low dimension with strong signal, high dimension (p = 10000) with weak signal and high dimensional with strong signal. Overall, the standard approach and linear predictor approach tend to select smaller $\lambda$ and select more variables than the other two approaches. Among all four of them, the Deviance residual approahc is the most conservative one.

@@

\par In this section, simulations studies were conducted to address the stability issue of the standard cross-validated likelihood. The standard approach is the most straighforward among all four methods that are presented in this paper. It also has the best predictive accuracy based on the simulation results in the previous section. However, this approach is much less widely used due to its unstability. When number of observed events in $D_k$ is really small, there would be insufficient number of events to construct the risk set for the partial likelihood. We thus conducted a simulation study varying the number of folds and censoring to see when the method would start to have convergence issue. In both studies, we set the number of observations to be n = 100. When we varied the censoring percentage, we fixed the number of folds K = 10; when we varied the number of folds, we fixed the censoring to be 10$\%$.
\par As is illustrated in Figure 3,  the standard approach start to have converge issue fairly quickly when censoring increases or when the number of folds increases. While the linear predictor approach performs as well as the standard approach in terms of prediction accuracy, the linear predictor approach is also as stable as the Verweij and Van Houwelingen's approach.

@@

    \subsection {Leave-One-Out Cross Validation}
	\par In this section, Leave-One-Out Cross Validation (LOOCV) were studied, in comparison with 10-fold CV. When first introduced, Verweij and Van Houwelingen's cross-validated partial likelihood was proposed so that LOOCV for Cox regression became feasible. It is impossible to carry out LOO cross-validation using the standard approach, because the partial likelihood cannot be built on the one left-out observation. While Verweij and Van Houwelingen's cross-validated partial likelihood solves the stability issue by aggregating more observations together, it is not an efficient way to evaluate the model fit. Simulation studies in Section 3.1 have illustrated that it tends to be conservative in variable selections and selects smaller models in various scenarios. This fact can be even more illustrated via the following simulation studies, where both 10-fold and LOOCV were conducted via Verweij and Van Houwelingen's approach, linear predictor and deviance residual approaches and 10 fold CV was conducted for the standard approach.
	\par As is illustrated in Figure 4, LOOCV selected models that have smaller MSE than 10-fold CV for all three CV approaches. As is shown in left and middle panels, LOOCV based on deviance residuals and Verweij and Van Houwelingen's cross-validated partial likelihood still perform more conservatively than the standard approach. Even if Verweij and Van Houwelingen's approach was proposed to allow LOOCV, the LOOCV based on Verweij and Van Houwelingen's approach does not surpass the 10-fold standard approach. On the other hand, the Linear Predictors also allows LOOCV, and the LOOCV based on Linear Predictors performs better than the standard approach.

@@

 \subsection {Cross-Validated C Index}

>>>>

\par Cross-validation is one of the most common methods used to select the appropriate $\lambda$ for penalized regression models. Suppose a data set $D$ of n observations is partitioned into $K$ folds: $D_{1}, D_{2}, ... D_{K}$. For a given $k \in \left\{1,2, ... , K\right\}$, set $T_{k} = D - D_{k}$. Then, we consider $T_{k}$ as the training set and $D_{k}$ as the test set. This manuscript is concerned with the question: how should one use the $kth$ fold $D_{k}$ to measure predictive accuracy based on partial likelihood? In the following sections, we use $L^{-k}$ to denote the partial likelihood that is built over data in $T_k$; use $L^{k}$ for partial likelihood built over data in $D_k$; and $L$ for partial likelihood built over the entire data set $D$.  The log partial likelihood is denoted by lower case $l$. Individual subject's contribution to the likelihood is denoted by $L_i$, where $i$ denotes the individual. Particularly of our interest, if $L^{-k}(\beta)$ is used in \eqref{eq:obj} to obtain penalized likelihood estimates using data in $T_k$, we use $\hat{\beta}^{-k}$ to denote the penalized estimates that are obtained.

@@

  %Need to update this section with the new baseline estimation method%
The fundamental challenge of conducting cross validation for cox regression is that the baseline hazard is not estimated from the model. Hence we proposed our next approach based on getting the baseline hazard $\hat{\Lambda}_{0}$. We would first obtain cross-validated linear predictors $\hat{\eta}^{cv}$ in the same way as the previous approach. With $\hat{\eta}^{cv}$,  a cross-validated version of baseline hazard $\hat{\Lambda}^{cv}_{0}$ that uses all observations can be estimated via Kalbfleisch and Prentice's method \citep{Kalbfleisch2011}.

As an analogue to the residual sum of squaires in linear regression, we considered using the sum of squared deviance residuals, the normalized form of Martingale residuals, to measure the model's predictive accuracy \citep{Therneau1990}. First proposed for model diagnosis, deviance residuals have also been used as a predictive accuracy measure in survival tree models \citep{Therneau2018}. Given that the baseline hazard and linear predictors are obtained via cross-validation, we can first obtain the cross-validated Martingale residual: 
	\begin{equation}
	\hat{M^{cv}_{i}} = \delta_{i} -\hat{\Lambda}^{cv}_{0}(t_{i})e^{\hat{\eta}^{cv}_{i}},
	\end{equation} 
where $\delta_{i}$ is the status of the $ith$ observation and $t_{i}$ is the time component of the $ith$ observation. The cross-validated deviance residuals can then be derived from the Martingale residuals: 
	\begin{equation} 
	d_{i} = sgn(\hat{M}^{cv}_{i})(-2(\hat{M}^{cv}_{i} + \delta_{i}log(\delta_{i} - \hat{M}^{cv}_{i})))^{1/2}.
	\end{equation}
The sum of squared cross-validated deviance residuals, $\sum_{i}\hat{d}_{i}^2$ are used as the cross validated error. We refer this approach as the \emph{cross-validated deviance residuals}.

@@

\par We first measure the distance between the fitted model and the true model via mean squared error of the coefficients. Suppose $\hat{\beta}(\lambda)$ is the set of coefficients estimated by a cox model with LASSO penalty at $\lambda$. Mean squared error $MSE$ is defined to be 
\begin{equation}
E(\hat{\beta}(\lambda) - \beta)^2
\end{equation}
For each generated data set, an oracle model would be fitted using Cox regression only upon variables that are set as non-zero in the data generating process. The resulted estimates would be denoted by $\hat{\beta}^{oracle}$. Then the models selected by the cross validation methods with $\lambda^{cv}$ would be compared to the oracle model via 
\begin{equation}
log\left\{ \frac{MSE(\hat{\beta}(\lambda^{cv}))}{MSE(\hat{\beta}^{oracle})} \right\}
\end{equation}
for each cross-validation selected $\lambda^{cv}$ in each generated data set. The results would be averaged over N replications. We take $log$ of the MSE ratio to correct the right skewness.

@@

\par While the MSE, Brier Score and Kullback-Leibler Score are good measures of the model, they are not very interpretable. Hence, we included Harrell's C Index as the last measure of the predictive accuracy\citep{HarrellJr1984}. The C Index is a rank-based statistic that measures the concordance between the linear predictor of the selected model and the observed outcome. Suppose we arbitrarily take two observation out of the data. If the observation that has a greater prognostic score also has a greater risk or shorter survival time until the event occur, then this would be considered as a concordant pair. C Index estimates of proportion of concordance pairs in the data set. C Index of 0.5 means the prediction is as good as flipping a coin and C Index of 1 means perfect concordance. We also computed Harrell's C Index upon the independent test set for all four models selected by cross-validation and averaged over all replications.

The simulation experiments were first conducted when the signal in the data was varied. In each simulated data set, there are n = 120 observations and p = 1000 covariates. 10$\%$ of the observations were censored. 10-fold cross-validation was implemented for all four methods. Number of non-zero $\beta$s was 10. The signal in the data set was varied by varying the magnitude of the $\beta$s from 0.4 to 0.9. For each scenario, 200 replications were used.

@@

\par Results of the simulation were illustrated in Figure 2. The x axis of the plots are the magnitude of the non-zero $\beta$ coefficients. The left panel compares the MSE ratios of selected models.  The y-axis represents the MSE ratios between the cross-validation selected models and the oracle model. The standard method has the smallest MSE ratio. The linear predictor approach's performance is also very close the standard approach. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater MSE. The middle panel compares the Brier scores of the models selected. The y-axis represents the Brier score. The standard method and the linear predictor approach have lower brier score across all levels of signals. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater Brier scores. The left panel compares Harrell's C of the models selected. The y-axis represents Harrell's C, which increases from around 0.6 to 0.8 as the coefficent size increases. The standard method and the linear predictor approach have slightly higher Harrell's C across all levels of signals, indicating better prediction accuracy. Overall, all four methods have very close performance .

@@

\caption{\label{tab:} Simulation Studies that Compare All Four Cross-Validation Methods Varying Dimension and Signal }
\centering
\begin{tabular}[t]{cccccccccc}
\toprule
 n& p& $\#$ Non-Zero & Signal & Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
150 & 50 & 5 & low & V VH  & 0.095 (0.028) & 1.457 (0.954) & 0.242 (0.013) & 0.678 (0.029) & 0.617 (0.034) \\
    &    &   &     & Standard  & 0.087 (0.030) & 1.459 (0.922) & 0.242 (0.013) & 0.678 (0.029) & 0.618 (0.032) \\
    &    &   &     & LinearPred  & 0.088 (0.025) & 1.433 (0.927) & 0.241 (0.013) & 0.677 (0.028) & 0.620 (0.029) \\
    &    &   &     & DevResid  & 0.132 (0.032) & 1.676 (1.019) & 0.248 (0.014) & 0.689 (0.030) & 0.601 (0.044) \\
\addlinespace
150 & 50 & 5 & strong & V VH  & 0.070 (0.011) & 1.733 (0.922) & 0.177 (0.012) & 0.527 (0.030) & 0.750 (0.014) \\
    &    &   &     & Standard  & 0.066 (0.012) & 1.688 (0.909) & 0.176 (0.012) & 0.526 (0.029) & 0.749 (0.014) \\
    &    &   &     & LinearPred  & 0.067 (0.011) & 1.695 (0.925) & 0.176 (0.012) & 0.526 (0.030) & 0.750 (0.014) \\
    &    &   &     & DevResid  & 0.110 (0.012) & 2.339 (0.868) & 0.187 (0.014) & 0.554 (0.033) & 0.750 (0.018) \\
\addlinespace
300 & 10000 & 20 & low & V VH  & 0.139 (0.021) & 3.463 (0.438) & 0.244 (0.015) & 0.681 (0.032) & 0.612 (0.051) \\
    &    &   &     & Standard  & 0.105 (0.027) & 3.350 (0.458) & 0.228 (0.021) & 0.646 (0.045) & 0.639 (0.05) \\
    &    &   &     & LinearPred  & 0.107 (0.026) & 3.360 (0.462) & 0.229 (0.021) & 0.648 (0.045) & 0.638 (0.049) \\
    &    &   &     & DevResid  & 0.139 (0.027) & 3.454 (0.447) & 0.243 (0.018) & 0.678 (0.038) & 0.610 (0.058) \\
\addlinespace
500 & 10000 & 20 & strong & V VH  & 0.072 (0.005) & 3.469 (0.480) & 0.162 (0.015) & 0.495 (0.036) & 0.784 (0.021) \\
    &    &   &     & Standard  & 0.056 (0.005) & 3.174 (0.504) & 0.153 (0.011) & 0.465 (0.029) & 0.782 (0.017) \\
    &    &   &     & LinearPred  & 0.057 (0.005) & 3.204 (0.498) & 0.153 (0.011) & 0.466 (0.029) & 0.783 (0.017) \\
    &    &   &     & DevResid  & 0.076 (0.005) & 3.545 (0.467) & 0.167 (0.015) & 0.508 (0.035) & 0.782 (0.022) \\
\bottomrule
\end{tabular}
\end{table}

\par Additional simulation studies were conducted for other four scenarios, which are a combination of different dimensions and signal in the data. The results are shown in Table 1. More specifically, we examined low dimension (p = 50) with weak signal, low dimension with strong signal, high dimension (p = 10000) with weak signal and high dimension with strong signal. Censoring was set to be 30$\%$. Overall, the standard approach and linear predictor approach tend to select smaller $\lambda$ and select more variables than the other two approaches. Among all four of them, the Deviance residual approahc is the most conservative one.

@@

\par In this section, simulation studies were conducted to address the stability issue of the standard cross-validated likelihood. The standard approach is the most straighforward among all four methods that are presented in this paper. It also has the best predictive accuracy based on the simulation results in the previous section. However, this approach is much less widely used due to its unstability. When number of observed events in $D_k$ is really small, there would be insufficient number of events to construct the risk set for the partial likelihood. We thus conducted a simulation study varying the number of folds and censoring to see when the method would start to have convergence issue. In both studies, we set the number of observations to be n = 100. When we varied the censoring percentage, we fixed the number of folds K = 10; when we varied the number of folds, we fixed the censoring to be 10$\%$. N = 200 replications were used to estimate the convergence probability.
\par As is illustrated in Figure 3,  the standard approach start to have converge issue fairly quickly when censoring increases or when the number of folds increases. While the linear predictor approach performs as well as the standard approach in terms of prediction accuracy, the linear predictor approach is also as stable as the Verweij and Van Houwelingen's approach.

@@

    \subsection {Leave-One-Out Cross Validation}
	\par In this section, we compared Leave-One-Out Cross Validation (LOOCV) with 10-fold cross validation. When first introduced, Verweij and Van Houwelingen's cross-validated partial likelihood was proposed so that LOOCV for Cox regression became feasible. While Verweij and Van Houwelingen's cross-validated partial likelihood solves the stability issue by aggregating more observations together, it does not seem to be an efficient way to evaluate the model fit based on results in Section 3.1. It tends to be conservative in variable selections and selects fewer variables in various scenarios. We further examined Verweij and Van Houwelingen's cross-validated partial likelihood under Leave-One-Out Cross Validation. In the following simulation studies, we used 10 fold cross-validated standard approach as our baseline for comparison. Then we conducted both 10-fold CV and LOOCV for Verweij and Van Houwelingen's approach, linear predictor approach and deviance residual approach.
	\par Results of the simulation experiment is illustrated in Figure 4.For all three methods, LOOCV selected models that have smaller MSE than 10-fold CV for all three CV approaches. As is shown in left and middle panels, LOOCV based on deviance residuals and Verweij and Van Houwelingen's cross-validated partial likelihood still perform more conservatively than the standard approach. Even if Verweij and Van Houwelingen's approach was proposed to allow LOOCV, the LOOCV based on Verweij and Van Houwelingen's approach does not surpass the 10-fold standard approach.

@@

 \subsection {Cross-Validated C Index}
\par In this section, we conducted simulation experiments to compare likelihood-based cross validation against AUC-based cross validation. While the focus of this manuscript is to study valid cross-validation methods for partial-likelihood-based models such as penalized Cox rgression, the methods proposed in this paper are not applicable to some other survival machine learning models that do not involve constructing a partial likelihood. In those cases, the cross-validated C Index, also called cross-validated AUC, is one of the most popular options \citep{Subramanian2011} \citep{Simon2011a}. As is proposed by Simon et al., cross-validated AUC is computed also based on cross-validated linear predictors or some other types of prognostic factors. Thus, it is of our curiosity to see which one has a better performance when those two approaches, likelihood-based and AUC-based, are both available after we obtain the cross-validated linear predictors.

\par We conducted simulations at both low dimension (p = 50) and high dimension (p = 1000), varying the signal in the data. Results of the simulations are illustrated in Figure 5. In general, the likelihood-based approach is more stable than the AUC-based cross validation approach. For MSE ratio and Brier Score, the likelihood approach tends to select more predictive models than the AUC-based approach. For the actual $\lambda$, it is interesting that the AUC-based approach is quite liberal and selected smaller $\lambda$s, which would yield models that contain more variables.
